Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation

### 2020-02-24 analysis/paper.Rmd

```{r load packages, include=TRUE}
#adding this line as a git test
#install specific versions of pakages called out in the paper
#require(devtools)
library(devtools)

#install_version("geomorph", version = "3.0.6", repos = "http://cran.us.r-project.org")
#install.packages("http://https://cran.r-project.org/src/contrib/Archive/geomorph/geomorph_3.0.6.tar.gz", repos=NULL, type="source")
library(geomorph) # geomorph 3.0.6

>>>>

```{r load packages, include=TRUE}
#adding this line as a git test
#install specific versions of pakages called out in the paper
#require(devtools)
library(devtools)
#install_version("geomorph", version = "3.0.6", repos = "http://cran.rstudio.com")
#install_version("geomorph", version = "3.0.6", repos = "http://cran.r-project.org")
#install.packages("http://https://cran.r-project.org/src/contrib/Archive/geomorph/geomorph_3.0.6.tar.gz", repos=NULL, type="source")
library(geomorph) # geomorph 3.0.6
